### 2019-07-29 1_introduction.tex
Tweak introduction.

To characterize the contribution of a programming model's runtime
system to application performance, and as an example of the novel studies that can be done
with Task Bench, we introduce a new metric called
\emph{minimum effective task granularity} (METG). Intuitively, for a given
workload, METG(50\%) is the smallest task granularity that maintains
at least 50\% efficiency, meaning that the application achieves at
least 50\% of the higest performance (in FLOP/s, B/s, or another
application-specific measure) that can be achieved on a given
machine. The efficiency bound in METG is a key innovation over
previous approaches, such as \emph{tasks per second} (TPS), that fail
to consider the amount of useful work peformed (if tasks are
non-empty~\cite{Canary16, Armstrong14}) or to perform any useful work at all (if tasks are empty~\cite{LegionTracing18}).

@@

We conduct a comprehensive comparative study of Task Bench
implementations in 15 different programming systems:
Chapel \cite{Chapel15}, Charm++ \cite{Charmpp93}, Dask \cite{Dask15}, MPI \cite{MPI}, MPI+X (OpenMP and CUDA),
OmpSs \cite{OmpSs11}, OpenMP \cite{OpenMPSpec40},
PaRSEC \cite{PARSEC13}, Realm \cite{Realm14}, Regent \cite{Regent15},
Spark \cite{Spark10}, StarPU \cite{StarPU11},
Swift/T \cite{Wozniak13}, TensorFlow \cite{TensorFlow15}, and
X10 \cite{X1005}. Using METG, we determine the baseline
runtime overhead of each system along with overheads associated with
increasing numbers of and/or variations in the pattern of dependencies. We
also explore each system's ability to scale, hide communication
overhead, and mitigate load imbalance.

>>>>

To characterize the contribution of runtime overheads
to application performance, and as an example of the novel studies that can be done
with Task Bench, we introduce a new metric called
\emph{minimum effective task granularity} (METG). Intuitively, for a given
workload, METG(50\%) is the smallest task granularity that maintains
at least 50\% efficiency, meaning that the application achieves at
least 50\% of the higest performance (in FLOP/s, B/s, or other
application-specific measure) achieved on a given
machine. The efficiency bound in METG is a key innovation over
previous approaches, such as \emph{tasks per second} (TPS), that fail
to consider the amount of useful work peformed (if tasks are
non-empty~\cite{Canary16, Armstrong14}) or to perform useful work at all (if tasks are empty~\cite{LegionTracing18}).

@@

We conduct a comprehensive comparative study of Task Bench
implementations in 15 programming systems:
Chapel \cite{Chapel15}, Charm++ \cite{Charmpp93}, Dask \cite{Dask15}, MPI \cite{MPI}, MPI+X (OpenMP and CUDA),
OmpSs \cite{OmpSs11}, OpenMP \cite{OpenMPSpec40},
PaRSEC \cite{PARSEC13}, Realm \cite{Realm14}, Regent \cite{Regent15},
Spark \cite{Spark10}, StarPU \cite{StarPU11},
Swift/T \cite{Wozniak13}, TensorFlow \cite{TensorFlow15}, and
X10 \cite{X1005}. Using METG, we find a number of factors---node
count, accelerators, and complex dependencies, among
others---individually or in combination contribute to an order of
magnitude or greater increase in METG, even in the most efficient
systems. While in the most simplified scenarios, some systems can
achieve a METG(50\%) of 390~ns, we show that a more realistic
bound for running nearly any application at scale is 100~\textmu{}s with
current technologies.

%% This implies that simplifying the application space too much
%% (e.g., by using trivial dependencies) risks overemphasizing the
%% importance of the lightweight mechanisms in such systems---a risk that
%% can be mitigated by using Task Bench's more complete coverage of the
%% space of application scenarios.

\zap{
Using METG, we determine the baseline
runtime overhead of each system along with overheads associated with
increasing numbers of and/or variations in the pattern of dependencies. We
also explore each system's ability to scale, hide communication
overhead, and mitigate load imbalance.
} % zap
